### 2019-04-08 Thesis/games.tex
Heidelberg library.

We also have the ability to create a new variable.
\begin{mathpar}
  \inferrule*{\Gamma,x\from \Var \ts M \from T}{\Gamma\ts \neww_T \lambda x.M\from T}
\end{mathpar}
The idea here is that if $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).

@@

  Indeed, if $s\vert_{B,D}\in P_{B\sequoid D}$ then $s$ begins with an initial $O$-move in $B$.  
  Then, \emph{since $\sigma$ is strict}, the next move in $s$ must be a move in $A$, and therefore $s\vert_{A,C}$ begins with a move in $A$.
  Since we also have $s\vert_{A,C}\in P_{A\tensor C}$, we must have that $s\vert_{A,C}\in P_{A\sequoid C}$.
\end{proof}
\begin{remark}
  This is the main place where we have used the assumption that $\sigma$ is a strict strategy: if we drop the strictness requirement from Definitionk \ref{DefSequoidOfStrategies}, then we get a valid (if nonsensical) strategy that has a partiality (`gives up') if playing according to $\sigma$ and $\tau$ would lead to it creating an invalid play.  
  But such a strategy would not satisfy the conclusion of Proposition \ref{PropWkCommutativeDiagram}, since $\sigma\tensor\tau;\wk_{B,D}$ would contain these extra plays where $\wk_{A,C};\sigma\sequoid\tau$ had `given up'.
\end{remark}
\begin{remark}
  Of course, we would \emph{like} to restate Proposition \ref{PropWkCommutativeDiagram} by saying that $\wk$ is some sort of natural transformation, but that doesn't make sense until we've shown that $\blank\sequoid\blank$ is a functor.
\end{remark}

@@

\begin{definition}[\cite{laird02}]
  A \emph{sequoidal category} $\C$ is given by
  \begin{itemize}
    \item a monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,\lunit,\runit$);
    \item a (strong) right action of $\C$ on a category $\C_s$; i.e., a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ together with natural isomorphisms
      \begin{mathpar}
        \passoc_{a,x,y}\from (a \sequoid x) \sequoid y \toisom a \sequoid (x \tensor y)
        \and
        \run_a \from a \toisom a \sequoid I
      \end{mathpar}
      that make the diagrams
      \begin{mathpar}
        \begin{tikzcd}[column sep=31pt]
          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}" yshift=1pt] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}" yshift=1pt]
              & a \sequoid ((x\tensor y) \tensor z)  \arrow[dl, "{a \sequoid \assoc_{x,y,z}}"] \\
          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}" yshift=1pt]
            & a \sequoid (x \tensor (y \tensor z))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \lunit_x}"] \arrow[d, "\run_a \sequoid x"']
            & a \sequoid (I \tensor x) \\
          (a \sequoid I) \sequoid x \arrow[ur, "{\passoc_{a,I,x}}"']
            &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \runit_x}"] \arrow[d, "\run_{a \sequoid x}"']
            & a \sequoid (x \tensor I) \\
          (a \sequoid x) \sequoid I \arrow[ur, "{\passoc_{a,x,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
      commute; and
    \item a lax morphism of actions from $\blank\sequoid\blank$ to the right tensor multiplication action $\blank\tensor\blank$ of $\C$ on itself; i.e., a functor $J\from \C_s \to \C$ and a natural transformation $\wk_{a,x} \from Ja \tensor x \to J(a \sequoid x)$ that makes the following diagrams commute.
      \begin{mathpar}
        \begin{tikzcd}[column sep=30pt]
          (Ja \tensor x) \tensor y \arrow[r, "{\wk_{a,x}\tensor y}"] \arrow[d, "{\assoc_{Ja,x,y}}"'] & J(a \sequoid x) \tensor y \arrow[r, "{\wk_{a\sequoid x,y}}"]
              & J((a \sequoid x) \sequoid y) \arrow[dl, "{J\passoc_{a,x,y}}"] \\
          Ja \tensor (x \tensor y) \arrow[r, "{\wk_{a,x\tensor y}}"]
            & J(a \sequoid (x \tensor y))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          Ja \arrow[r, "J\run_a"] \arrow[d, "\runit_{Ja}"']
            & J(a \sequoid I) \\
          Ja \tensor I \arrow[ur, "{\wk_{a,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
  \end{itemize}
  \label{DefSequoidalCategory}
\end{definition}
\begin{remark}
  The definitions of \emph{lax action} can be found at the start of chapter \ref{SecParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.  
  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in chapter \ref{SecParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.  
  A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
\end{remark}

@@

\begin{figure}
  \begin{mathpar}
    \inferrule*{ }{\Gamma,s\ts c \converges c,s}
    \and
    \inferrule*{\Gamma,s \ts M \converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x] \converges c,s''}{\Gamma,s \ts MN \converges c,s''}
    \and
    \inferrule*{\Gamma,s \ts M(\Y M) \converges c,s'}{\Gamma,s \ts \Y M \converges c,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges n,s'}{\Gamma,s\ts \suc M \converges n+1,s'}
    \\\and
    \inferrule*{\Gamma,s\ts M \converges n+1,s'}{\Gamma,s\ts \pred M \converges n,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges 0,s'}{\Gamma,s\ts \pred M \converges 0,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges \skipp,s' \\ \Gamma,s'\ts N \converges c,s''}{\Gamma,s \ts M;N \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges \true,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges \false,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges 0,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges n+1,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
    \and
    \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges n,s' \\ \Gamma,s' \ts V \converges x,s''}{\Gamma,s\ts V \gets E \converges \skipp,(s''\vert x \mapsto n)}
    \and
    \inferrule*[right={$s'(x)=n$}]{\Gamma,s\ts V \converges x,s'}{\Gamma,s\ts !V \converges n,s'}
    \and
    \inferrule*{\Gamma,x\from\Var,(s\vert x\mapsto 0)\ts M \converges c,(s'\vert x\mapsto n)}{\Gamma,s\ts \neww \lambda x.M \converges c,s'}
    \and
    \inferrule*{\Gamma,s\ts E \converges n,s' \\ \Gamma,s'\ts V \converges \mkvar W R,s'' \\ \Gamma,s'' \ts Wn \converges \skipp,s'''}
    {\Gamma,s \ts V\gets E \converges \skipp,s'''}
    \and
    \inferrule*{\Gamma,s\ts V \converges \mkvar W R,s' \\ \Gamma,s'\ts R \converges n,s''}{\Gamma,s\ts !V \converges n,s''}
  \end{mathpar}
  \caption[Operational semantics for Idealized Algol.]{Operational semantics for Idealized Algol. See \cite{RusssThesis} and \cite{SamsonGuyIAActive}.}
  \label{FigIaOpSem}
\end{figure}

@@

\begin{proposition}
  Suppose that $\Gamma,s\ts M\converges c,s'$.  
  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
  \[
    \Gamma_1,s^{(1)}\ts M_1 \opto \cdots \opto \Gamma_n,s^{(n)}\ts M_n\,,
    \]
  and $s^{(n)}\vert_{\Gamma}=s'$.
  \label{PropBigToSmall}
\end{proposition}
\begin{proof}
  Induction on the derivation of $\Gamma,s\ts M\converges c,s'$.  
  Since most of the cases are similar, we cover a selection for illustration.

@@

\begin{lemma}
  The relation $\oopto$ betwen triples $\Gamma,s\ts M$ preserves the composite
    \oc\deno{s};\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_{\Gamma}}\,.

@@

            &  \deno{T}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{T} \sequoid (\Gamma+0_\Delta)}"] \\

@@

            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,,}

@@

  where $\Gamma+0_\Delta\from \oc \V_\Gamma \to \oc \V_{\Gamma,\Delta}$ is the composite
    \oc \V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc \V_\Gamma \tensor I \xrightarrow{\oc\V_\Gamma\tensor \oc0} \oc\V_\Gamma \tensor \oc S_\Delta \xrightarrow{\oc\V_\Gamma\tensor \cell^\Delta} \oc \V_\Gamma \tensor \oc \V_\Delta \to \oc \V_{\Gamma,\Delta}\,;
  i.e., the morphism given by initializing new storage cells to $0$ for all the new variables in $\Delta$.

@@

        \oc\V_\Gamma \xrightarrow{\Gamma + 0_x} \oc\V_{\Gamma,x} \xrightarrow{\Lambda\inv(\deno{\Gamma \ts \lambda x.M})} \deno{T}\,,

@@

      where $\Gamma+0_x$ is as defined in the statement of this Lemma.
      Of course, $\Lambda\inv(\deno{\Gamma\ts \lambda x.M})=\deno{\Gamma,x\ts M}$.

      Next, we claim that we have a commutative diagram

@@

        \begin{tikzcd}
          \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "{\oc\langle S_\Gamma,0\rangle}"']
            & \oc \V_\Gamma \arrow[d, "\Gamma+0_x"] \\
          {\oc S_{\Gamma,x}} \arrow[r, "{\cell^{\Gamma,x}}"]
            & {\oc \V_{\Gamma,x}\,.}

@@

      Indeed, we have the diagram

@@

        \begin{tikzcd}[column sep=2pt, row sep=20pt]
          \oc S_\Gamma \arrow[r] \arrow[dddd, "{\oc\langle S_\Gamma,0\rangle}"' description]
            &[5pt] \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell\tensor \cdots \tensor \cell"] \arrow[d, "\runit" description]
              &[10pt] \oc\Varr \tensor \cdots \tensor \oc\Varr \arrow[r] \arrow[d, "\runit" description]
                & \oc\V_\Gamma \arrow[d, "\runit" description] \\
            & \oc \bN \tensor \cdots \tensor \oc\bN \tensor I \arrow[r, "\cell \tensor \cdots \tensor \cell \tensor I" yshift=6pt] \arrow[ddd, "\oc\bN \tensor \cdots \tensor \oc\bN \tensor \oc0" description]
              & \oc \Varr \tensor \cdots \tensor \oc\Varr\tensor I \arrow[d, "\oc\Varr \tensor \cdots \tensor \oc\Varr \tensor I" description] \arrow[r]
                & \oc\V_\Gamma \tensor I \arrow[d, "\oc\V_\Gamma\tensor\oc0" description] \\

@@

              & \oc\Varr \tensor \cdots \tensor \oc\Varr\tensor \oc\bN \arrow[r] \arrow[dd, "\oc\Varr\tensor\cdots\tensor\oc\Varr\tensor\cell" description]
                & \oc\V_\Gamma \tensor \oc\bN \arrow[d, "\oc\V_\Gamma\tensor\cell" description] \\

@@

                & \oc\V_\Gamma\tensor\oc\Varr \arrow[d] \\
          {\oc S_{\Gamma,x}} \arrow[r]
            & \oc\bN \tensor\cdots \tensor\oc\bN \tensor\oc\bN \arrow[uur, "\cell\tensor\cdots\tensor\cell\tensor\oc\bN" {description, near start}] \arrow[r, "\cell\tensor\cdots\tensor\cell\tensor\cell"' yshift=-3pt]
              & \oc\Varr \tensor \cdots\tensor\oc\Varr \tensor \oc\Varr \arrow[ur] \arrow[r]
                & {\oc\V_{\Gamma,x}\,.}

@@

      Now the diagram in Figure \ref{FigSoundnessOoptoNew} shows us that the conclusion of the lemma is satisfied for this rule.
          \begin{tikzcd}[ampersand replacement=\&, column sep=50pt, row sep=40pt]
            I \arrow[r, "\oc\deno s"] \arrow[d, "\oc(\deno s\times 0)"']
              \& \oc S_\Gamma \arrow[dl, "{\oc\langle S_\Gamma,0\rangle}" description] \arrow[dr, "\mu_{S_\Gamma}" description] \arrow[r, "\cell^\Gamma" description]
                \& \oc \V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}"]
                    \& \oc \V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "(\Gamma + 0_x)\tensor\oc\V_\Gamma"] \arrow[ddddllll, "(\Gamma+0_x)\tensor(\Gamma+0_x)" description, bend left=12] \\
            {\oc S_{\Gamma,x}} \arrow[dr, "\mu_{S_\Gamma}" description] \arrow[d, "{\cell^{\Gamma,x}}"']
                \& \oc S_\Gamma \tensor \oc S_\Gamma \arrow[urr, "\cell^{\Gamma} \tensor \cell^{\Gamma}" {description, near start}, bend left=10] \arrow[dl, "{\oc\langle S_\Gamma,0\rangle\tensor\oc\langle S_\Gamma,0\rangle}" description]
                    \& {\oc\V_{\Gamma,x}\tensor\oc\V_\Gamma} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\V_\Gamma}"] \\
            {\oc\V_{\Gamma,x}} \arrow[dd, "{\mu_{\V_{\Gamma,x}}}"']
              \& {\oc S_{\Gamma,x}\tensor\oc S_{\Gamma,x}} \arrow[ddl, "{\cell^{\Gamma,x}\tensor\cell^{\Gamma,x}}"' {description, near start}, bend right=10]
                    \& \deno T \tensor \oc\V_{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}"] \arrow[ddll, "\deno T \tensor (\Gamma + 0_x)" description, bend left=8] \\
                    \& \deno T \sequoid \oc\V_\Gamma\arrow[d, "{\deno T \sequoid (\Gamma + 0)}"] \\
            {\oc \V_{\Gamma,x} \tensor \oc \V_{\Gamma,x}} \arrow[rr, "{\deno{\Gamma,x\ts M}\tensor \oc\V_{\Gamma,x}}"]
                \& {\deno T \tensor \oc\V_{\Gamma,x}} \arrow[rr, "{\wk_{\deno T,\oc\V_{\Gamma,x}}}"]
                    \& {\deno T\sequoid\oc\V_{\Gamma,x}}
        \caption{The reduction $\Gamma,s\ts\neww\lambda x.M\oopto\Gamma,x,(s\vert x\mapsto 0)\ts M$ satisfies the conclusion of Lemma \ref{LemSoundnessOopto}.}

@@

      Now the diagram in Figure \ref{FigSoundnessOoptoContext} tells us that each
        \oc\deno{s};\cell^{x,\Gamma};\mu_{\V_{x,\Gamma}};(\deno{x,\Gamma\ts M}\tensor\oc\V_{x,\Gamma});\wk_{\deno T,\oc\V_{x,\Gamma}}\,\text{--}
      i.e., the composites we are trying to show are preserved by the $\oopto$ relation -- may be written as

@@

      and so is determined by the composite

@@

      i.e., the composite that we would get if $\Gamma$ were empty.
      This tells us that we can assume that $\Gamma$ is the empty context when we want to deal with these two cases.

@@

              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt, dotted]}, bend left=5] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
                \& \deno{T} \tensor (\oc\Varr \tensor \oc\V_\Gamma) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\V_\Gamma}}" description, dotted]

@@

>>>>

We also have the ability to create a new variable.
\begin{mathpar}
  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma,x\from \Var \ts M \from T}{\Gamma\ts \neww_T \lambda x.M\from T}
\end{mathpar}
The idea here is that if $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).

@@

  Indeed, if $s\vert_{B,D}\in P_{B\sequoid D}$ then $s$ begins with an initial $O$-move in $B$.  
  Then, \emph{since $\sigma$ is strict}, the next move in $s$ must be a move in $A$, and therefore $s\vert_{A,C}$ begins with a move in $A$.
  Since we also have $s\vert_{A,C}\in P_{A\tensor C}$, we must have that $s\vert_{A,C}\in P_{A\sequoid C}$.
\end{proof}
\begin{remark}
  This is the main place where we have used the assumption that $\sigma$ is a strict strategy: if we drop the strictness requirement from Definition \ref{DefSequoidOfStrategies}, then we get a valid (if nonsensical) strategy that has a partiality (`gives up') if playing according to $\sigma$ and $\tau$ would lead to it creating an invalid play.  
  But such a strategy would not satisfy the conclusion of Proposition \ref{PropWkCommutativeDiagram}, since $\sigma\tensor\tau;\wk_{B,D}$ would contain these extra plays where $\wk_{A,C};\sigma\sequoid\tau$ had `given up'.
\end{remark}
\begin{remark}
  Of course, we would \emph{like} to restate Proposition \ref{PropWkCommutativeDiagram} by saying that $\wk$ is some sort of natural transformation, but that doesn't make sense until we've shown that $\blank\sequoid\blank$ is a functor.
\end{remark}

@@

\begin{definition}[\cite{laird02}]
  A \emph{sequoidal category} $\C$ is given by
  \begin{itemize}
    \item a symmetric monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,$ $\lunit$, $\runit$, $\sym$);
    \item a (strong) right action of $\C$ on a category $\C_s$; i.e., a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ together with natural isomorphisms
      \begin{mathpar}
        \passoc_{a,x,y}\from (a \sequoid x) \sequoid y \toisom a \sequoid (x \tensor y)
        \and
        \run_a \from a \toisom a \sequoid I
      \end{mathpar}
      that make the diagrams
      \begin{mathpar}
        \begin{tikzcd}[column sep=31pt]
          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}" yshift=1pt] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}" yshift=1pt]
              & a \sequoid ((x\tensor y) \tensor z)  \arrow[dl, "{a \sequoid \assoc_{x,y,z}}"] \\
          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}" yshift=1pt]
            & a \sequoid (x \tensor (y \tensor z))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \lunit_x}"] \arrow[d, "\run_a \sequoid x"']
            & a \sequoid (I \tensor x) \\
          (a \sequoid I) \sequoid x \arrow[ur, "{\passoc_{a,I,x}}"']
            &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \runit_x}"] \arrow[d, "\run_{a \sequoid x}"']
            & a \sequoid (x \tensor I) \\
          (a \sequoid x) \sequoid I \arrow[ur, "{\passoc_{a,x,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
      commute; and
    \item a lax morphism of actions from $\blank\sequoid\blank$ to the right tensor multiplication action $\blank\tensor\blank$ of $\C$ on itself; i.e., a functor $J\from \C_s \to \C$ and a natural transformation $\wk_{a,x} \from Ja \tensor x \to J(a \sequoid x)$ that makes the following diagrams commute.
      \begin{mathpar}
        \begin{tikzcd}[column sep=30pt]
          (Ja \tensor x) \tensor y \arrow[r, "{\wk_{a,x}\tensor y}"] \arrow[d, "{\assoc_{Ja,x,y}}"'] & J(a \sequoid x) \tensor y \arrow[r, "{\wk_{a\sequoid x,y}}"]
              & J((a \sequoid x) \sequoid y) \arrow[dl, "{J\passoc_{a,x,y}}"] \\
          Ja \tensor (x \tensor y) \arrow[r, "{\wk_{a,x\tensor y}}"]
            & J(a \sequoid (x \tensor y))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          Ja \arrow[r, "J\run_a"] \arrow[d, "\runit_{Ja}"']
            & J(a \sequoid I) \\
          Ja \tensor I \arrow[ur, "{\wk_{a,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
  \end{itemize}
  \label{DefSequoidalCategory}
\end{definition}
\begin{remark}
  The definitions of \emph{lax action} can be found at the start of chapter \ref{SecParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.  
  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in chapter \ref{SecParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.  
  A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
\end{remark}

@@

\begin{figure}
  \vspace{-27pt}
  \begin{mathpar}
    \inferrule*{ }{\Gamma,s\ts c \converges c,s}
    \and
    \inferrule*{\Gamma,s \ts M \converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x] \converges c,s''}{\Gamma,s \ts MN \converges c,s''}
    \and
    \inferrule*{\Gamma,s \ts M(\Y M) \converges c,s'}{\Gamma,s \ts \Y M \converges c,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges n,s'}{\Gamma,s\ts \suc M \converges n+1,s'}
    \\\and
    \inferrule*{\Gamma,s\ts M \converges n+1,s'}{\Gamma,s\ts \pred M \converges n,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges 0,s'}{\Gamma,s\ts \pred M \converges 0,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges \skipp,s' \\ \Gamma,s'\ts N \converges c,s''}{\Gamma,s \ts M;N \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges \true,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges \false,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges 0,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges n+1,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
    \and
    \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges n,s' \\ \Gamma,s' \ts V \converges x,s''}{\Gamma,s\ts V \gets E \converges \skipp,(s''\vert x \mapsto n)}
    \and
    \inferrule*[right={$s'(x)=n$}]{\Gamma,s\ts V \converges x,s'}{\Gamma,s\ts !V \converges n,s'}
    \and
    \inferrule*{\Gamma,x\from\Var,(s\vert x\mapsto 0)\ts M \converges c,(s'\vert x\mapsto n)}{\Gamma,s\ts \neww \lambda x.M \converges c,s'}
    \and
    \inferrule*{\Gamma,s\ts E \converges n,s' \\ \Gamma,s'\ts V \converges \mkvar W R,s'' \\ \Gamma,s'' \ts Wn \converges \skipp,s'''}
    {\Gamma,s \ts V\gets E \converges \skipp,s'''}
    \and
    \inferrule*{\Gamma,s\ts V \converges \mkvar W R,s' \\ \Gamma,s'\ts R \converges n,s''}{\Gamma,s\ts !V \converges n,s''}
  \end{mathpar}
  \caption[Operational semantics for Idealized Algol.]{Operational semantics for Idealized Algol. See \cite{RusssThesis} and \cite{SamsonGuyIAActive}.}
  \label{FigIaOpSem}
\end{figure}

@@

\begin{proposition}
  Suppose that $\Gamma,s\ts M\converges c,s'$.  
  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n=\Gamma,\Delta$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
  \[
    \Gamma_1,s^{(1)}\ts M_1 \opto \cdots \opto \Gamma_n,s^{(n)}\ts M_n\,,
    \]
  and $s^{(n)}\vert_{\Gamma}=s'$.
  \label{PropBigToSmall}
\end{proposition}
\begin{proof}
  Induction on the derivation of $\Gamma,s\ts M\converges c,s'$.  
  Since most of the cases are similar, we cover a selection for illustration.

@@

\begin{definition}
  Let $\Gamma,s\ts M\from T$ be a term with store.  
  Then the \emph{sequoidal denotation} $\seqdeno{\Gamma,s\ts M}$ is the composite
  \[
    I \xrightarrow{\deno s} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\oc\V_\Gamma} \deno T \tensor\oc\V_\Gamma \xrightarrow{\wk_{\deno T,\oc\V_\Gamma}} \deno T \sequoid \oc\V_\Gamma\,.
    \]
\end{definition}

\begin{lemma}
  The relation $\oopto$ betwen triples $\Gamma,s\ts M$ preserves the sequoidal denotation $\seqdeno{\Gamma,s\ts M}$.

@@

            &  \deno{T}\sequoid \oc\V_\Gamma \\

@@

            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,.} \arrow[u, "\deno{T}\sequoid\oc\pr_\Gamma"']

@@

  I.e., if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, then $\seqdeno{\Gamma,s\ts M} = \seqdeno{\Gamma,\Delta,s'\ts N};\oc\pr_\Gamma$.

@@

        \oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\oc\V_\Gamma\tensor (0;\cell)} \oc\V_\Gamma \tensor \oc\Varr \to \oc\V_{\Gamma,x} \xrightarrow{\Lambda\inv(\deno{\Gamma \ts \lambda x.M})} \deno{T}\,,

@@

      where, of course $\Lambda\inv(\deno{\Gamma\ts\lambda x.M})=\deno{\Gamma,x\ts M}$, and that the projection $\pr_\Gamma \from \oc\V_{\Gamma,x}$ is a right inverse for the composite $\runit_{\oc\V_\Gamma};(\oc\V_{\Gamma}\tensor(0;\cell));\cong$, since we have a commutative diagram

@@

        \begin{tikzcd}[column sep=50pt]
          \oc\V_\Gamma \arrow[r, "\runit_{\oc\V_\Gamma}"] \arrow[d, Rightarrow, no head]
            & \oc\V_\Gamma \tensor I \arrow[r, "\oc\V_\Gamma\tensor(0;\cell)"] \arrow[d, "\id_{\oc\V_\Gamma\tensor I}" description]
              & \oc\V_\Gamma \tensor \oc\Varr \arrow[d] \arrow[dl, "\oc\V_\Gamma\tensor()" description] \\
          \oc\V_\Gamma
            & \oc\V_\Gamma \tensor I \arrow[l, "\runit\inv"']
              & {\oc\V_{\Gamma,x}\,.} \arrow[ll, "\oc\pr_\Gamma", bend left=20]

@@

      Then we may prove this case using the commutative diagram in Figure \ref{FigSoundnessOoptoNew}.

@@

          \begin{tikzcd}[column sep=34pt, row sep=30pt]
            I \arrow[r, "\oc\deno s"] \arrow[d, "{\oc\langle\deno s,0\rangle}" description]
              &[5pt] \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
                &[-5pt] \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"] \arrow[d, "\mu_{\V_\Gamma}" description]
                  & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\runit_{\oc\V_\Gamma};(\oc\V_\Gamma\tensor (0;\cell));\cong" {description, xshift=-16pt}] \\
            {\oc S_{\Gamma,x}} \arrow[ur, "\oc\pr_\Gamma" description] \arrow[d, "{\cell^{\Gamma,x}}" description]

@@

                & \oc\V_\Gamma\tensor\oc\V_\Gamma
                  & {\oc\V_{\Gamma,x}\tensor\oc\V_\Gamma} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\V_\Gamma}" description] \arrow[l, "\pr_\Gamma\tensor\oc\V_\Gamma"'] \\
            {\oc\V_{\Gamma,x}} \arrow[uurr, "\oc\pr_\Gamma" description] \arrow[d, "{\mu_{\V_{\Gamma,x}}}"]

@@

                  & \deno T \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}" description] \\
            {\oc\V_{\Gamma,x}\tensor\oc\V_{\Gamma,x}} \arrow[uurr, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma" {description, pos=0.7}] \arrow[uurrr, "{\V_{\Gamma,x}\tensor\pr_\Gamma}" {description, pos=0.7}] \arrow[r, "{\deno{\Gamma,x\ts M}\tensor\oc\V_{\Gamma,x}}"' yshift=-3pt]
              & {\deno T \tensor \oc\V_{\Gamma,x}} \arrow[r, "{\wk_{\deno T,\oc\V_{\Gamma,x}}}"' yshift=-3pt]
                & {\deno T \sequoid \oc\V_{\Gamma,x}} \arrow[r, "\deno T \sequoid\pr_\Gamma"' yshift=-3pt]
                  & \deno T \sequoid\oc\V_\Gamma

@@

        \caption{The conclusion of Lemma \ref{LemSoundnessOopto} holds for the $\neww$ rule.}

@@

      Now the diagram in Figure \ref{FigSoundnessOoptoContext} tells us that each $\seqdeno{\Gamma,x,s\ts M}$ may be written as the composite

@@

      and so is completely determined by the value of the composite

@@

      i.e., the sequoidal denotation $\seqdeno{x,s\vert_x\ts M}$.

      This tells us that we can assume that $\Gamma$ is the empty context, so that the rules take on the form
        x,s\ts x\gets n \oopto x,(x\mapsto n)\ts \skipp
        x,s \ts \oc x \oopto x,s\ts s(x)\,.

@@

              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt]}, bend left=5, dotted] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
                \& \deno{T} \tensor (\oc\Varr \tensor \oc\V_\Gamma) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\V_\Gamma)}}" description, dotted]

@@

Now that we have dealt with the base rules, we can move on to the full relation $\opto$.
